Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2019-08-12 paper/referee_reply2.txt

The submitted draft is a very minor revision from a previously submitted manuscript that had reached the "minor revisions" stage of the MNRAS referee process. However, we missed the deadline for resubmitting the second revision, and in accord with an email exchange with Joop Schaye, we are submitting this paper as a new manuscript.

In the intervening time since the last round of minor revisions, we have pursued two closely related directions of research that we had originally thought might be included in our revisions: 1. Studying the IllustrisTNG predictions for size-dependent lensing, and 2. new SDSS measurements of size-dependent lensing. In the end, both extensions turned out to be more involved than we anticipated, and so we have decided to pursue these directions in separate papers. We apologize for the inconvenient timing and hope that our tardiness will not adversely influence the review of our manuscript.

As the original referee was clearly an expert in the relevant domain who has already provided a thorough review of the paper, we request that the same referee review the current manuscript, if possible. To facilitate review of our resubmission, we have included below our response to the second referee report, and as supplementary material we have uploaded a redline PDF showing the changes made in the second round of revisions.

-----

### 2019-08-12 paper/submitted_tarball/galsize_paper.tex
Tarballed up source files for final submission

Observations of two-point galaxy clustering, $\wproj(\rproj),$ have historically been used to place tight constraints on many features of the galaxy--halo connection, such as its $\mstar-$dependence \citep{moster_etal10,leauthaud_etal11,reddick_etal13,skibba_etal15}, dependence on luminosity \citep{kravtsov_etal04, tasitsiomi_etal04,vale_ostriker04,vale_ostriker06,tinker_etal05,cacciato_etal13}, broadband color \citep{coil_etal08,zehavi_etal11,guo_etal11,hearin_watson13}, and star-formation rate \citep{wang_etal07,tinker_etal13,watson_etal14}. In the present work, we exploit the constraining power of $\wproj(\rproj)$ to test empirical models connecting galaxy stellar mass and size to the properties of the galaxy's parent dark matter halo.

@@

We measure $\wproj(\rproj)$ separately for large and small subsamples for four different thresholds in $\log_{10}\mstar/\msun:$ 9.75, 10.25, 10.75, and 11. We follow standard practice \citep[e.g.,][]{zehavi_etal11} and throw out all galaxies with $z<z_{\rm min}=0.02$ to minimize lightcone effects; to minimize the effect of redshift evolution we also throw out galaxies with redshift $z \geq z_{\rm max}=0.1,$ including cases where a volume-limited sample would be attainable out to higher redshift. We refer to Table \ref{table:data} for a summary of our volume-limited galaxy samples.

@@

We include a prescription for supplementing the ordinary {\tt Rockstar} subhalo catalog with disrupted subhalos, so that some of our model galaxies inhabit subhalos that are no longer resolved and do not appear in the standard publicly available catalog (``orphan galaxies"). Orphans play an important in our model due to the sensitivity of $\rhalf$-dependent clustering upon the satellite fraction. In our fiducial model whose results are shown in the main body of the text, half of the disrupted subhalos are selected prior to application of SHAM. We explore alternative treatments of orphans in the appendix.

@@

Our methodology is closely aligned with \citet{somerville_etal17}, who studied the empirical modeling features that are necessary to recover the tight scatter in the observed $\mean{\rhalf}{\mstar}$ relation. By building models where $\rhalf$ is set by halo spin $\lambda_{\rm halo}$, it was found in \citet{somerville_etal17} that the level of intrinsic scatter about $\langle\lambda_{\rm halo}\vert\mhalo\rangle$ in dark matter halos is at least as large as the scatter about $\langle\rhalf\vert\mstar\rangle$ seen in observed galaxies. Their conclusions are consistent with previous findings \citep[e.g.,][]{dejong_lacey00, gnedin_etal07}, but employ modern forward-modeling methods that enable using two-point clustering as constraining data as we have here. In our approach, the level of scatter about the $\langle\rhalf\vert\mstar\rangle$ relation receives a contribution both from the scatter in the stellar-to-halo mass relation, $\langle\mstar\vert\mhalo\rangle,$ as well as from scatter about the $\langle\rhalf\vert\mhalo\rangle$ relation; the fiducial value chosen for the former level of scatter was motivated by the results in \citet{reddick_etal13} to ensure our fiducial model has reasonable satellite fractions; the fiducial value for the second contribution to the model's stochasticity was motivated by \citet{somerville_etal17}. Both modeling choices are germane to ongoing follow-up work discussed in \S\ref{sec:future}, in which we will systematically test the large-scale structure implications of the assumption that $\rhalf^{\rm disk}\propto\lambda_{\rm halo}$ using forward-modeling methods analogous to those advocated for in \citet{somerville_etal17} and employed here.

>>>>

Observations of two-point galaxy clustering, $\wproj(\rproj),$ have historically been used to place tight constraints on many features of the galaxy--halo connection, such as its $\mstar-$dependence \citep{moster_etal10,behroozi_etal10,leauthaud_etal11,reddick_etal13,skibba_etal15}, dependence on luminosity \citep{kravtsov_etal04, tasitsiomi_etal04,vale_ostriker04,vale_ostriker06,tinker_etal05,cacciato_etal13}, broadband color \citep{coil_etal08,zehavi_etal11,guo_etal11,hearin_watson13}, and star-formation rate \citep{wang_etal07,tinker_etal13,watson_etal14}. In the present work, we exploit the constraining power of $\wproj(\rproj)$ to test empirical models connecting galaxy stellar mass and size to the properties of the galaxy's parent dark matter halo.

@@

We measure $\wproj(\rproj)$ separately for large and small subsamples for four different thresholds in $\log_{10}\mstar/\msun:$ 9.75, 10.25, 10.75, and 11. We follow standard practice \citep[e.g.,][]{zehavi_etal11} and throw out all galaxies with $z<z_{\rm min}=0.02$ to ensure the applicability of our use of the small-angle approximation in calculating two-point clustering; to minimize the effect of redshift evolution we also throw out galaxies with redshift $z \geq z_{\rm max}=0.1,$ including cases where a volume-limited sample would be attainable out to higher redshift. We refer to Table \ref{table:data} for a summary of our volume-limited galaxy samples.

@@

We include a prescription for supplementing the ordinary {\tt Rockstar} subhalo catalog with disrupted subhalos, so that some of our model galaxies inhabit subhalos that are no longer resolved and do not appear in the standard publicly available catalog (``orphan galaxies"). Orphans play an important role in our model due to the sensitivity of $\rhalf$-dependent clustering upon the satellite fraction. In our fiducial model whose results are shown in the main body of the text, half of the disrupted subhalos are selected prior to application of SHAM. We explore alternative treatments of orphans in the appendix.

@@

Our methodology is closely aligned with \citet{somerville_etal17}, who studied the empirical modeling features that are necessary to recover the tight scatter in the observed $\mean{\rhalf}{\mstar}$ relation. By building models where $\rhalf$ is set by halo spin $\lambda_{\rm halo}$, it was found in \citet{somerville_etal17} that the level of intrinsic scatter about $\langle\lambda_{\rm halo}\vert\mhalo\rangle$ in dark matter halos is at least as large as the scatter about $\langle\rhalf\vert\mstar\rangle$ seen in observed galaxies. Their conclusions are consistent with previous findings \citep[e.g.,][]{dejong_lacey00, gnedin_etal07}, but employ modern forward-modeling methods that enable using two-point clustering as constraining data as we have here. In our approach, the level of scatter about the $\langle\rhalf\vert\mhalo\rangle$ relation receives a contribution both from the scatter in the stellar-to-halo mass relation, $\langle\mstar\vert\mhalo\rangle,$ as well as from scatter about the $\langle\rhalf\vert\mstar\rangle$ relation; the fiducial value chosen for the former level of scatter was motivated by the results in \citet{reddick_etal13} to ensure our fiducial model has reasonable satellite fractions; the fiducial value for the second contribution to the model's stochasticity was motivated by \citet{somerville_etal17}. Both modeling choices are germane to ongoing follow-up work discussed in \S\ref{sec:future}, in which we will systematically test the large-scale structure implications of the assumption that $\rhalf^{\rm disk}\propto\lambda_{\rm halo}$ using forward-modeling methods analogous to those advocated for in \citet{somerville_etal17} and employed here.
